\section{Introduction}
    More and more people make use of GitHub to host their Open Source Software (OSS)\cite{github-2013}. 
    GitHub is not only a place were people share their software, it has also become a `social network' for software developers because of its social features. \cite{dabbish-2012} 
    One of those social features is `starring' a project. Users can show their appreciation for a project by giving it a  star and many of GitHub's own rankings are also based on the amount of stars a project has.\cite{github-stars-2016} 
    Therefore one can state that the amount of stars gives an indication of how many people appreciate the project.
    
    However, there might be several factors that can be related to the amount of stars of a project. 
    One can think of the functionality that the project offers, but what about projects that offer more or less the same functionality but have a greatly different amount of stars? Other factors such as popularity of the topic of the project, it being easy to use, e.g. a library that can be added, and more, can all have influence.
    
    This paper will be looking at the stars given to OSS projects and whether certain factors are related to the amount of stars a project can possibly get, and if there are key points to focus on when aiming at having the most stars as possible.
    Those keypoints might be characteristics they can influence; maybe attracting a popular developer to your project helps a lot. However, another project characteristic that might be related to the number of stars is the number of forks. 
    Unfortunately, that is not a feature that can be influenced by a project owner.
    
    This research will be of help for developers who want to gain more stars for their projects.
    On top of that, a dataset with interesting features concerning two thousand projects hosted at GitHub can be of interest for other researchers in the mining software repositories field.
    

    %\todo{
    %    \begin{itemize}
    %        \item What are stars?
    %        \item Why are stars cool?/what do they indicate?
    %        \item How is it possible to research them?
    %    \end{itemize}
    %}

%Uit 2011, maargoed toen al populair, dus tegenwoordig moeten zo nog wel meer hebben:
%https://github.com/blog/841-those-are-some-big-numbers
%https://github.com/blog/1204-notifications-stars

%%Popularity: (TODO: add more of those as actual references??)
%https://github.com/blog/1724-10-million-repositories
%https://github.com/blog/685-one-million-repositories
%http://readwrite.com/2011/06/02/github-has-passed-sourceforge

%%%Language popularity:
%https://github.com/blog/2047-language-trends-on-github
%https://www.researchgate.net/profile/Christophe_Giraud-Carrier/publication/228993701_Programming_language_trends_in_open_source_development_An_evaluation_using_data_from_all_production_phase_sourceforge_projects/links/0fcfd510c5d5b16f8a000000.pdf /???????

%http://www.iculture.nl/swift-populariteit-github-programmeertalen/
%https://www.githubarchive.org
