\documentclass[10pt,conference]{IEEEtran}

\usepackage{hyperref}

\usepackage{graphicx}
\usepackage{caption}
\usepackage{xcolor}
\usepackage{flushend}

\newcommand\todo[1]{\textcolor{red}{#1}}

\title{How to win a star on GitHub}

\author{
    \IEEEauthorblockN{Michel Kraaijeveld}
    \IEEEauthorblockA{Delft University of Technology\\
                    Delft, the Netherlands\\
                    Email: j.c.m.kraaijeveld@student.tudelft.nl\\}
    \and
    \IEEEauthorblockN{Tom den Braber}
    \IEEEauthorblockA{Delft University of Technology\\
                        Delft, the Netherlands\\
                    Email: t.d.denbraber@student.tudelft.nl}
}

\begin{document}

\maketitle
\IEEEdisplaynontitleabstractindextext

\begin{abstract}
	GitHub is a very successful open source software platform on which many projects are hosted.
	Since stars are included in the rankings on GitHub, they can be a good aspects to focus on when trying to stand out with a project.
	In this paper, a new dataset is presented based on GitHub data which consists of two thousand projects and multiple features.
	The dataset is created by using the GHTorrent project and making manual adjustments, such as adding domains to each of the projects.
	The paper also contains a model - that is used in combination with the created dataset - to predict the amount of stars for an open source software project.
	The model was applied by using multiple learning algorithms to find out whether prediction of stars is possible and to what extent.
	Experiments show that the model is able to predict the amount of stars with a high $R^2$ value, depending on the learning algorithm used.
	In combination with Random Forest and a log-scaled dataset, the model was able to obtain an $R^2$ value of 0.88.
	It shows that the predicted amount of stars is close to the actual number of stars.
\end{abstract}

\input{sections/introduction}

%\input{sections/background}

\input{sections/problem-description}

\input{sections/methodology}

\input{sections/evaluation}

\input{sections/results}

\input{sections/related-work}

\input{sections/future-work}

\input{sections/conclusion}
\newline

\bibliography{references}{}
\bibliographystyle{ieeetr}

\end{document}
